\begin{center}
    \section*{Abstract}
\end{center}
A concerning amount of children is being touched by autism day by day and it is not often early detected in their childhood. Austism is much treatable if treated early in the toddler stage of life thus preventing suffer in the later stages of the life and our thesis tries to offer help in that area. Certain repitive actions are greatly observed in the toddlers affected with autism and AI models are trained and evaluated to recognise them hence the models in our thesis can later anylize the suspicious footages of child and evaluate them via prior training and refer them if treatment is needed thus detecting autism. Our thesis relies on the behaviour related physical traits of a austism child like hand flapping, finger clipping, head touching, spining and tilting. So, we visited a special childrens school and with the help of its authority we found over 50 autism affected children and collected footages from them when they were doing the poses by our android mobile devices. Then we preprocessed those pose related videos and feed them to AI models to do classification work and also to train those exact models to recognize these five traits so that whenever a new video of a suspicious child will be tested on these models it can classify those certrain traits like how much hand flapping or finger clipping or head touching was detected while testing. This is no clinical recognised study but an effort to help autism finding so that it can suggest whether clinical attention is needed and the rest depends on the concerning parents. But we collected austim affected childrens data from actually going to the related fields to train our models so from a reliable point of accuracy our trained model can indeed find autism related patterns in childrens video footages later suggesting a evalution via prior experience only to help in early screen if austism exists.